Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-18 paper.tex
minor changes to section 5

\textbf{(RP6)} development of automated synthesis approaches that are algorithmically and numerically sound, in order to handle (control) software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.

>>>>

\textbf{(RP6)} development of automated synthesis approaches that are algorithmically and numerically sound, in order to handle (control) software that is tightly coupled with physical environments, by considering uncertain models and FWL effects.
